A boundary-integral framework to simulate \\ viscous erosion of a porous medium

### 2018-04-10 docs/methods/erosion_methods.tex
NM

We have combined two accurate and stable numerical methods to simulate two-dimensional viscous erosion in a porous medium.  First, a BIE formulation of the incompressible Stokes equations discretizes only the boundary of the bodies and resolves their non-negligible interactions.  Second, the bodies are evolved with the so-called {\thL} variables to avoid tangling and distortion of the mesh.  The resulting numerical method is spectral in space, second-order in time, and is accelerated with the fast multipole method.

%Using slender body theory and flow past a wedge, the method is verified against analytical results for the area, opening angle, and total drag of a single eroding body.  Then, for multi-body erosion with a realistic pressure drop boundary condition, we compute the area fraction, flow rate, and total drag across a channel.  We observe that erosion leads to channelization, and this reduces the resistance more than would be expected if the area fraction were reduced by simply scaling down the size of the bodies.  This indicates that the area fraction can not fully characterize flow in eroding porous media since the interactions between the bodies plays a role in the resistance.

>>>>

We have combined two accurate and stable numerical methods to simulate two-dimensional viscous erosion in a porous medium. First, a BIE formulation of the incompressible Stokes equations discretizes only the boundaries and resolves non-negligible interactions between bodies. This Stokes solver enables computation of the surface shear stress, which dictates the erosion rate of solid material. To advance solid boundaries forward in time, we use the {\thL} framework, which prevents tangling and distortion of the mesh that would otherwise lead to numerical instability. The resulting method is accurate (spectral in space, second-order in time), numerically stable, and accelerated via the fast multipole method.

Analytical results for the case of a single eroding body provide a stringent benchmark for our simulation. In particular, by appealing to the principle of long-time uniform stress, we predict a front/rear corner of 102, which matches closely the value measured in the simulations. Scaling laws for the asymptotic rate of area and drag reduction also match the simulation.

Simulations of multiple eroding bodies reveals even more complex behavior. As in the single body case, we witness the formation of sharp corners, but not in locations that are easily predictable. Furthermore, bodies tend to form flat faces in places where there was initially near contact, which leads to the appearance of straight channels between bodies. The overall resistance of the porous network declines rapidly, which we attribute the channelization process.
